SemanticPaint

### 2015-12-04 cv3d_seminar/paper.tex
finished contentwise, needs to be shortened and polished

\section{Putting it All Together}
\section{Results}
\section{Future Work}
\section{Conclusions}

% \section{Pipeline}
% \section{Mean-Field Inference}
% \section{Streaming Random Forest}
% \section{Voxel-Oriented Patch Features}
% \section{Qualitative Results}
% \section{Quantitative Results}
% \section{Discussion}
% \section{Conclusions}

% 	\begin{table}[!hbt]
% 		% Center the table
% 		\begin{center}
% 		% Title of the table
% 		\caption{Simulation Parameters}
% 		\label{tab:simParameters}
% 		% Table itself: here we have two columns which are centered and have lines to the left, right and in the middle: |c|c|
% 		\begin{tabular}{|c|c|}
% 			% To create a horizontal line, type \hline
% 			\hline
% 			% To end a column type &
% 			% For a linebreak type \\
% 			Information message length & $k=16000$ bit \\
% 			\hline
% 			Radio segment size & $b=160$ bit \\
% 			\hline
% 			Rate of component codes & $R_{cc}=1/3$\\
% 			\hline
% 			Polynomial of component encoders & $[1 , 33/37 , 25/37]_8$\\
% 			\hline
% 		\end{tabular}% 		\end{center}
% 	\end{table}
% 
% 	\begin{figure}[!hbt]
% 		% Center the figure.
% 		\begin{center}
% 		% Include the eps file, scale it such that it's width equals the column width. You can also put width=8cm for example...
% 		\includegraphics[width=\columnwidth]{plot_tf}
% 		% Create a subtitle for the figure.
% 		\caption{Simulation results on the AWGN channel. Average throughput $k/n$ vs $E_s/N_0$.}
% 		Define the label of the figure. It's good to use 'fig:title', so you know that the label belongs to a figure.
% 		\label{fig:tf_plot}
% 		\end{center}
% 	\end{figure}

>>>>

\section{Putting it All Together}

    The user comes into a room and touches a table uttering a label at the same time. Then, he touches a chair giving another label. He switches into test mode and goes into another room. All tables and chair are marked by the system accordingly. It works by feeding Voxel Oriented Patches associated with each pixel to the Streaming Random Forest, which learn to predict voxel categories in an online fashion. User interactions are facilitated by a Conditial Random Field that models the label distribution. An efficient mean-field algorithm, which amortizes classification of the whole scene among several frames, is used on top of it to smooth predicted labels.

\section{Results}
  Each part of the pipeline is evaluated separately. Several video sequences were recorded to evaluate segmentation and VOP features. A set of keyframe covering the whole scene from each sequence was hand-labeled to create groudtruth data. They were further projected into the 3D volume, resulting in 4176, 12346, 7583, 8916 frames for \emph{LivingRoom}, \emph{Kitchen}, \emph{Bedroom}, \emph{Desk} sequences respectively, of wich around a third was used for testing. Table \ref{fig:segm_results} summarises segmantation results. User interaction gives very accurate labeling, but it is pertinent to single object instances only. SRF prediction works quite well and is improved by the inference algorithm. Table \ref{fig:vop_results} compares VOPs against other features. The numbers reflect the percentage of correctly classified pixels with SRF using different features. VOP clearly outperforms all other features. $\Delta$ RGB mean stands for the mean difference of two randomly selected patches.

\begin{table}[!ht]	\label{fig:segm_results}
 \center
 \caption{Segmentation Results.}
 \begin{tabular}{c|c|c|c|c|c}
  \textbf{Component} & \textbf{LivingRoom} & \textbf{Bedroom} & \textbf{Kitchen} & \textbf{Desk} & \textbf{Average} \\ \hline
  User Interaction & 99.35\% & 97.61\% & 96.09\% & 97.73\% & 97.7\% \\ 
  Forest Prediction & 94.57\% & 88.31\% & 82.58\% & 90.29\% & 88.94\% \\
  Final Inference & 96.26\% & 95.19\% & 90.69\% & 95.55\% & 94.42\%
 \end{tabular}
\end{table}

\begin{table}[!ht]	\label{fig:vop_results}
 \center
 \caption{Comparison of VOP against other features.}
 \begin{tabular}{c|c|c|c|c|c}
  \textbf{Feature} & \textbf{LivingRoom} & \textbf{Bedroom} & \textbf{Kitchen} & \textbf{Desk} & \textbf{Average} \\ \hline
  VOP & \textbf{94.57\%} & \textbf{88.31\%} & 82.58\% & \textbf{90.29\%} & \textbf{88.94\%} \\
  $\Delta$ RGB mean & 80\% & 71.84\% & 76.29\% & 73.42\% & 75.39\% \\
  Depth probe& 77.54\% & 61.79\% & \textbf{84.9\%} & 68.9\% & 73.06\% \\
  Color Probe& 56.39\% & 65.68\% & 60.77\% & 60.74\% & 60.9\% \\
  SURF & 43.74\% & 67.12\% & 57\% & 58.13\% & 56.5\% \\
  SPIN & 58.77\% & 43.22\% & 48.41\% & 36.1\% & 46.63\% \\
 \end{tabular}
\end{table}

  SRF was compared against Online Random Forests (ORF) \cite{online_forest} and Hoeffding trees (HT) \cite{htree}. In order to simulate non-IID data, a dataset of 300 objects of 51 categories \cite{dataset} was used. One revolution of each object was recorded with an RGBD camera from three different viewpoints. Online setting was created by sequentially adding new categories. Two thirds of each viewpoint of each object is used for training. Results are summarized by figure \ref{fig:srf_results}. SRF clearly outperforms its competitors.

\begin{figure}[!ht]	 \label{fig:srf_results}
 \center
 \includegraphics[width=0.75\textwidth]{figures/srf_results}
 \caption{Comparison of Streaming Random Forest against Online Random Forest and Hoeffding Trees.}
\end{figure}

\section{Discussion}

  This paper contributes an interactive system that enables users to create customized models of 3D enviornments. It can be used to gather groundtruth for large-scale visual recognition systems, robot navigation and to aid partially sighted people. There are some limitations, however. Use of the system is now restricted to simple, indoor scenes. Computational load increases with the size of the scene while prediction accuracy drops with the number of object categories. There are also some failure cases as shwon in figure \ref{fig:failures}.

\begin{figure}[!ht]	 \label{fig:failures}
 \center
 \includegraphics[width=0.75\textwidth]{figures/failures}
 \caption{Failure cases.}
\end{figure}

Combing colour and depth data requires careful sensor calibration. Lack thereof results in misclassification at object boundaries. Also strong changes of lighting conditions impair classification ability at certain viewpoints. What is more, no global context is used for classification, which could be improved if some prior knowledge were introduced. There are two disjoint modes: training and testing, which limits possible use cases.

\section{Summary}

\section{Future Work}

  - introducing prior
  - improving user interaction system (verbal priors)
  - improving scalability
  - using pure geometrical features
  - moving to outdoor settings
  - better scaling
